Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex
Forgot an addition to the bibtex.  Finished last proof draft.

  \begin{case}[if]
    \todo{}
  \end{case}

@@

  \begin{case}[lift-if]
    \todo{}
  \end{case}

>>>>

  \begin{case}[if]
    $e = \textsf{if } v \: e_1 \: e_2$ and $e' = e_i$ where $i$ is determined by
    the value of $v$.  \textsc{E-If}'s premises include $\typeRule{pc
    \sqcup l}{e_i}{t}$ for $i \in \{1, 2\}$ and $l \guards t$, which follows
    from Lemma~\ref{lem:weakening}.
  \end{case}

@@

  \begin{case}[lift-if]
    $e = \text{if } <v_1 | v_2> \: e_1 \: e_2$ and $e' = e_i$ for some $i \in
    \{1, 2\}$ in this case.  Applying Lemma~\ref{lem:guard} to the first premise
    of \textsc{E-If} gives $l' \in H$ and $l' \guards t$.  Applying
    Lemma~\ref{lem:projection} to the intial premises of \textsc{E-If} and using
    the result and applying \textsc{E-If} gives $\typeRule{pc \sqcup l}{e_i}$.
    We can then apply \textsc{E-Bracket} to get the goal.
  \end{case}
